\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%%%%%%%%%%%%%
\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features. Self-adaptive mesh refinement methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}. In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) as the simulation evolves in time and space focusing resolution where is necessary.

\red{Blablabla ... improve text ...} ... {\it The mesh adaptive algorithm embedded in the Fluidity/ICFERST model utilises a metric tensor field dependent on solution interpolation error-estimates \red{(talk about a posteriori errors and a short description of the mesh adaptivity algorithm)}\blue{(ref mesh adaptivity paper of 1995)} which locally control size and shape of elements in the metric. Mesh optimisation, based on XXX simulated annealing, is able to generate unstructured finer mesh grid in regions where flow properties change faster and coarser mesh grid in regions  where properties does not change so quickly.  }

>>>>

%%%%%%%%%%%%%
\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features. Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces. These lead to a mesh that conforms to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.

Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}. In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space. There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity). Detailed description and analysis of these methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book,plewa_book,frey_book}.

The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model
\red{Blablabla ... improve text ...} ... {\it The mesh adaptive algorithm embedded in the Fluidity/ICFERST model utilises a metric tensor field dependent on solution interpolation error-estimates \red{(talk about a posteriori errors and a short description of the mesh adaptivity algorithm)}\blue{(ref mesh adaptivity paper of 1995)} which locally control size and shape of elements in the metric. Mesh optimisation, based on XXX simulated annealing, is able to generate unstructured finer mesh grid in regions where flow properties change faster and coarser mesh grid in regions  where properties does not change so quickly.  }
